VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-10 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added examples --- still needs loads of work

%%%%%%%%%%%%%%%%%%%%
 \usepackage{hyperref} % Editor will use to create hyperlinks %
 %%% but if the author has problems with the above style file,
 %%% then comment the line \usepackage{hyperref} or replace by this below:
 % \usepackage{upref}
%%%%%%%%%%%%%%%%%%%%

@@

The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral. It, however, does tell us that a given Riemann-Stieltjes integral can be converted into another equivalent Riemann-Stieltjes integral. This newly obtained integral can then be converted into a Cavalieri integral. We explain this in more detail in Section~\ref{}.

@@

\section{Left-sided Riemann-Liouville Fractional Integral}
In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
\begin{equation}
_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
\end{equation}
Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$. It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ to denote our upper integration limit in Eq.~\ref{??}). 
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_{a'}^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_{a'}^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
\begin{equation}
_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
\end{equation}
The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
Eq.~\eqref{eq:frac_integral} reduces to:
\begin{equation}
_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
\end{equation}

@@

Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis. Moreover, let $A_{t}^{\alpha}$ denote the 
area of $R_t^{\alpha}$. When we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$. Moreover, $R_t^{\alpha}$ can be decomposed into an infinite number of infinitesimals, each one of them being a translation of $a_t^{\alpha}(y)$. The shape of the aforementioned infenitesimals are non-static, since their shape depend on the value of $t$ and $\alpha$. Stated differently, we can approximate $A_{t}^{\alpha}$ via a Cavalieri sum, the shape of the integration strips used within this sum will be determined by $a_t^{\alpha}(y)$. In the limit this sum will approach $_{a'}I_t^{\alpha}\,f(t)$. The shape of the aforementioned integration strips are also non-static. Their shape is determined by the value of $t$ and $\alpha$. These assertions are all direct consequences of Eq ??.

>>>>

%%%%%%%%%%%%%%%%%%%%
 \usepackage{hyperref} % Editor will use to create hyperlinks %
 %%% but if the author has problems with the above style file,
 %%% then comment the line \usepackage{hyperref} or replace by this below:
 % \usepackage{upref}
 \usepackage{xfrac}
%%%%%%%%%%%%%%%%%%%%

@@

The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral. It, however, does tell us that a given Riemann-Stieltjes integral can be converted into another equivalent Riemann-Stieltjes integral. This newly obtained integral can then be converted into a Cavalieri integral. We explain this in more detail in Section~\ref{} via an example.

@@

\section{Left-sided Riemann-Liouville Fractional Integral}
In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
\begin{equation}
_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
\end{equation}
Please note that in this paper from this point onwards our variable of integration will be $\tau$ instead of $x$. It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ as our upper integration limit). 
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_{a'}^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_{a'}^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
\begin{equation}
_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
\end{equation}
The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
Eq.~\eqref{eq:frac_integral} reduces to:
\begin{equation}
_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
\end{equation}

@@

The assertions below all follow from Eq ??. Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis. Moreover, let $A_{t}^{\alpha}$ denote the 
area of $R_t^{\alpha}$. When we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$. Moreover, $R_t^{\alpha}$ can be decomposed into an infinite number of infinitesimals, each one of them being a translation of $a_t^{\alpha}(y)$. The shape of the aforementioned infenitesimals are non-static, since their shape depend on the value of $t$ and $\alpha$. Stated differently, we can approximate $A_{t}^{\alpha}$ via a Cavalieri sum, the shape of the integration strips used within this sum will be determined by $a_t^{\alpha}(y)$. In the limit this sum will approach $_{a'}I_t^{\alpha}\,f(t)$. The shape of the aforementioned integration strips are also non-static. Their shape is determined by the value of $t$ and $\alpha$.

\section{Examples}
Consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
_0I_t^{\alpha} f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. Let us first convert 
the above integral into a Riemann-Stieltjes integral (see Section~\ref{??}):
\begin{equation}
_0I_t^{\alpha} f(t)=\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
\end{equation}
We can now convert the above Riemann-Stieltjes integral into a Cavalieri integral (see Section~\ref{??}):
\begin{equation}
\label{eq:ex1}
_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
\end{equation}
with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$. Note, it turns out that for this example $a=a'=C=0$.

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
\label{fig:geo1}
\end{figure}

% \noindent
% Since Eq.~\eqref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}). It can be interpreted as the area obtained by summing together the areas of an infinite 
% number of infinitesimals whose shape is determined by $\alpha$ and $t$, i.e. these infinitesimals have to be translations of $b_t^{\alpha}(y)$. The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$. 
% There is one thing, however, which remains unclear: in what way do $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e. how does the value of $\alpha$ and $t$ affect the shape of $b_t^{\alpha}(y)$. 
% We will answer this question by working through a detailed example.\\

%using two basic steps. First off, we will fix the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$. We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
%We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
%they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.

\noindent
If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\label{eq:ex1_specific}
_0I_{10}^{\sfrac{4}{5}} f(t) = \int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau = A_{10}^{\sfrac{4}{5}}. 
\end{equation}
Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$. The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}. It is the largest of all the regions depicted in the right-most panel of Fig.~\ref{fig:geo1}. Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{??}). Furthermore, note that dashed grey curves in the right-most panel of Fig.~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\

% We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
% construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
% If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach the Cavalieri integral in Eq.~\eqref{eq:ex1_specific}, i.e. $A_{10}^{\sfrac{4}{5}}$.  
% Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
% of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$. Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.  Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Fig.~\ref{fig:geo1}. 
% The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines. Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\sfrac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\

%We have thus verified that we can employ the Cavalieri integral in Eq.~\eqref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
%Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
%We can, therefore, interpet Eq.~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
%of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.

\noindent
Let $\mathsf{T}=\{2,4,6,8,10\}$. Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
right-most edge of $R_{t}^{\alpha}$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. When we evaluate Eq.~\eqref{eq:ex1} we obtain $A_{t}^{\alpha}$ (see Section~\ref{??}). The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}. The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
the larger the $t$-value is that is associated with it.\\

\noindent
As mentioned in Section~\ref{}, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals. The infinitesimals that make up the regions in Fig.~\ref{fig:geo1} are translations of each region's right edge. The following observations can now be made by inspecting Fig.~\ref{fig:geo1}: 
\begin{description}
 \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one another, i.e. $b_{t}^{\alpha_1}(y)\neq b_{t}^{\alpha_2}(y)$ when $\alpha_1\neq\alpha_2$. 
 \item[Effect of $t$] The dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one another. The gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are, therefore, not translations of one another.
\end{description}

We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig.~\ref{fig:geo1}. Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape. The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between the aforementioned curves (if their 
sizes are ignored). The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not correlated).\\

%In the case of $\alpha$: the gray-tinted solid curves depicted in each panel are not equal to one-another. Similarly, in the case of $t$: the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.

\begin{table}[h!]
\centering
\caption{Curves obtained by evaluating Eq.~\eqref{eq:ex1} and Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
\label{tab:eval}
\begin{tabular}{||c|| c| c||} 
 \hline
 $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
 \hline\hline
 \rule{0pt}{2.5ex}
 $0$ & $t$ & $\sqrt{t}$  \\  
 \rule{0pt}{2.5ex}
 $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\sfrac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\sfrac{7}{10}}$  \\ 
 \rule{0pt}{2.5ex}
 $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\sfrac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\sfrac{9}{10}}$  \\
 \rule{0pt}{2.5ex}
 $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\sfrac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\sfrac{11}{10}}$  \\ 
 \rule{0pt}{2.5ex}
 $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\sfrac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\sfrac{13}{10}}$  \\ 
 \rule{0pt}{2.5ex}
 $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\sfrac{3}{2}}$  \\ [1ex]
 \hline
 \end{tabular}
\end{table}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{func_eval1.eps}
\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
\label{fig:eval1}
\end{figure}

\noindent
If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}) we obtain the curves in the 
left-most column of Table~\ref{tab:eval}. These curves are depicted in Fig.~\ref{fig:eval1}.
The area of the regions depicted in Fig.~\ref{fig:geo1} are also plotted in Fig.~\ref{fig:eval1} using circular markers. As expected, the circular markers in Fig.~\ref{fig:eval1} that correspond to the areas of the regions in Fig.~\ref{fig:eval1}  
associated with a particular choice of $\alpha$ (i.e. regions depicted in a particular panel of Fig.~\ref{fig:geo1}) fall on the curve in Fig.~\ref{fig:eval1}; associated with the same choice of $\alpha$. Moreover, note that we have adopted the 
same coloring scheme in Fig.~\ref{fig:geo1} and Fig.~\ref{fig:eval1}. Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{fig:eval1} can be associated with which regions in Fig.~\ref{fig:geo1}.
To summarize, Fig.~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular infinitesimal-based geometric interpretation of Eq.~\eqref{eq:ex1}. Moreover, Fig.~\ref{fig:eval1} corroborates this geometric interpretation.\\

\noindent
Let us now consider a different fractional integral:
\begin{equation}
\label{eq:ex2}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig.~\ref{fig:geo2}. 
If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}. 
These curves are depicted in Fig~\ref{fig:eval2}.
The validity of the non-static non-rectangular infinitesimal-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{geo_int2.eps}
\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
\label{fig:geo2}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{func_eval2.eps}
\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
\label{fig:eval2}
\end{figure}
